Future challenges for Research Software Engineering

### 2025-03-17 future_challenges_for_RSEng.tex
Add bibliography

% Article frontmatter
% ===================
\title{Future challenges for Research Software Engineering} % Title of the article
%\short{} % Short title of the article (optional)
\author{
Florian Goth\autref{1},
Leyla Jael Castro\autref{1},
Gerasimos Chourdakis\autref{1},
Simon Christ\autref{1},
Jeremy Cohen\autref{1},
Jean-Noël Grad\autref{1},
Magnus Hagdorn\autref{1},
Toby Hodges\autref{1},
Jan Linxweiler\autref{1},
Frank Löffler\autref{1},
Michele Martone\autref{1},
Jan Philipp Thiele\autref{1},
Nick del Grosso\autref{1}
} % Authors and references to addresses
\institute{Fantasy University\autlabel{1}} % Institutes with labels
\abstract{Admittedly, it’s still only 2025 and we are actually stillworking on establishing Research Software Engineering
as a new domain with the hope of ensuring that it gets the recognition it deserves.
And while it is certainly too early to already herald the end of RSEng,
we should acknowledge that the future is in constant flux and
it is worthwhile to discuss how RSEng will/could change in response to these upcoming challenges in an open discussion.} % Abstract of the article
\keywords{Keywords go here.} % Keywords for the article

@@

% Main part of your article
% =========================
\section{Introduction}
This opinion article stems from a Bof session at deRSE25 in Karsruhe. Therefore it stems from a discussion
among the participants of this workshop and hence cannot claim that it represents the entire deRSE community.
Nevertheless we hope, that we succeeded in writing up something that
\begin{itemize}
\item you like to read,
\item gives you something to think about,
\item motivates you to work on creating this better future.
\end{itemize}

@@

% Bibliography with BibTeX
% ========================
\bibliographystyle{eceasst}
%\bibliography{}

>>>>

% Article frontmatter
% ===================
\title{Future challenges for Research Software Engineering} % Title of the article
%\short{} % Short title of the article (optional)
\author{
Florian Goth\texorpdfstring{\autref{1}}{},
Leyla Jael Castro\texorpdfstring{\autref{1}}{},
Gerasimos Chourdakis\texorpdfstring{\autref{1}}{},
Simon Christ\texorpdfstring{\autref{1}}{},
Jeremy Cohen\texorpdfstring{\autref{1}}{},
Jean-Noël Grad\texorpdfstring{\autref{1}}{},
Magnus Hagdorn\texorpdfstring{\autref{1}}{},
Toby Hodges\texorpdfstring{\autref{1}}{},
Jan Linxweiler\texorpdfstring{\autref{1}}{},
Frank Löffler\texorpdfstring{\autref{1}}{},
Michele Martone\texorpdfstring{\autref{1}}{},
Jan Philipp Thiele\texorpdfstring{\autref{1}}{},
Nick del Grosso\texorpdfstring{\autref{1}}{}
} % Authors and references to addresses
\institute{Fantasy University\autlabel{1}} % Institutes with labels
\abstract{Admittedly, it’s still only 2025 and we are actually stillworking on establishing Research Software Engineering
as a new domain with the hope of ensuring that it gets the recognition it deserves.
And while it is certainly too early to already herald the end of RSEng,
we should acknowledge that the future is in constant flux and
it is worthwhile to discuss how RSEng will/could change in response to these upcoming challenges in an open discussion.} % Abstract of the article
\keywords{Keywords go here.} % Keywords for the article

@@

% Main part of your article
% =========================
\section{Introduction}
This opinion article stems from a Bof session at deRSE25 in Karlsruhe\cite{Goth2025EndRSEng}. Therefore it stems from a discussion
among the participants of this workshop and hence cannot claim that it represents the entire deRSE community.
Nevertheless we hope, that we succeeded in writing up something that
\begin{itemize}
\item you like to read,
\item gives you something to think about,
\item motivates you to work on creating this better future.
\end{itemize}

@@

% Bibliography with BibTeX
% ========================
\bibliographystyle{eceasst}
\bibliography{bibliography/bibliography,extra}
